---
title: "p8105_hw_jz3900"
author: "ELisajava"
date: "2024-09-21"
output: github_document
---

This is my R Markdown file for P8105 HW1 (jz3900)

Load the tidyverse function for HW1
```{r library, message=FALSE}
library(tidyverse)
```
# Problem 1

The task involves providing a brief description of the penguins dataset, which includes:

* The data in the dataset, including the names and values of important variables

* The size of the dataset

* The mean flipper length

* Creating a scatterplot


Load the penguins dataset from the "palmerpenguins" package:

```{r}
data("penguins", package = "palmerpenguins")
```

## Names of the dataset
```{r}
names(penguins)
```
It shows that the names in the penguins dataset are: bill_depth_mm, bill_length_mm, body_mass_g, flipper_length_mm, island, sex, species, year.

## The size of the dataset
The size of the dataset is `r nrow(penguins)` rows and `r ncol(penguins)` columns

## The mean flipper length

The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`

## Creating scatterplot

Use this code to create a scatterplot with flipper_length_mm on the y-axis and bill_length_mm on the x-axis, using different colors for each species:

```{r}
#create a scatterplot
scatterplot = ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point(na.rm = TRUE) +
  labs(
    title = "scatterplot of flipper_length_mm (y) vs bill_length_mm (x)",
    x = "Bill Length (mm)",
    y = "Flipper Length (mm)"
  ) +
  theme_classic()
print(scatterplot)
# save the scatterplot
ggsave(filename = "scatterplot_flipper_vs_bill.png", plot = scatterplot, width = 8, height = 8)
```
