---
title: "p8105_hw_jz3900"
author: "ELisajava"
date: "2024-09-21"
output: github_document
---

This is my R Markdown file for P8105 HW1 (jz3900)

Load the tidyverse function for HW1
```{r library, message=FALSE}
library(tidyverse)
```
# Problem 1

The task involves providing a brief description of the penguins dataset, which includes:

* The data in the dataset, including the names and values of important variables

* The size of the dataset

* The mean flipper length

* Creating a scatterplot


Load the penguins dataset from the "palmerpenguins" package:

```{r}
data("penguins", package = "palmerpenguins")
```

## Names of the dataset
```{r}
names(penguins)
```
It shows that the names in the penguins dataset are: bill_depth_mm, bill_length_mm, body_mass_g, flipper_length_mm, island, sex, species, year

## The size of the dataset
The size of the dataset is `r nrow(penguins)` rows and `r ncol(penguins)` columns

## The mean flipper length

The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`

## Creating scatterplot

Use this code to create a scatterplot with flipper_length_mm on the y-axis and bill_length_mm on the x-axis, using different colors for each species:

```{r}
#create a scatterplot
scatterplot = ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point(na.rm = TRUE) +
  labs(
    title = "scatterplot of flipper_length_mm (y) vs bill_length_mm (x)",
    x = "Bill Length (mm)",
    y = "Flipper Length (mm)"
  ) +
  theme_classic()
print(scatterplot)
# save the scatterplot
ggsave(filename = "scatterplot_flipper_vs_bill.png", plot = scatterplot, width = 8, height = 8)
```


# Problem 2
This problem involves creating a data frame that includes:

* A random sample of size 10 from a standard normal distribution
* A logical vector indicating whether the elements of the sample are greater than 0
* A character vector of length 10
* A factor vector of length 10 with three distinct factor levels
* attempt to calculate the mean of each variable in the data frame.

## Create data frame
### First, create four variables describes in the problem 2:

Create a random sample:
```{r}
random_samp = rnorm(10)
```

Create a logical vector:
```{r}
logical_vec = random_samp > 0
```

Create a character vector of length 10:
```{r}
char_vec = sample(c("1","2","3"), size=10, replace = TRUE)
```

Create a factor vector:
```{r}
factor_vec = factor(sample(c("Low", "Medium", "High"), size = 10, replace = TRUE))
```

### Then put these vector into the dataframe:
```{r}
HW1_df=
  tibble(
    random_samp=random_samp,
    logical_vec=logical_vec,
    char_vec=char_vec,
    factor_vec=factor_vec
  )
```

## Take mean of each variable
Next, attempt to calculate the mean of each variable in the data frame (HW1_df) using the pull function from the tidyverse package.
```{r mean_pull}
mean(pull(HW1_df, random_samp))
mean(pull(HW1_df, logical_vec))
mean(pull(HW1_df, char_vec))
mean(pull(HW1_df, factor_vec))
```

The result shows that we can take the mean of a numeric variable and logical variable, but can't take the mean of character and factor variables.

Then, use as.numeric function to character, and factor variables, in order to try to convert them to numeric variable.
```{r}
char_vec_numeric=as.numeric(pull(HW1_df, char_vec))
factor_vec_numeric=as.numeric(pull(HW1_df, factor_vec))
```
Try to caclulate the mean of the converted variable:
```{r}
mean_char_vec=mean(char_vec_numeric)
mean_factor_vec=mean(factor_vec_numeric)
```
```{r, echo=FALSE}
cat("The mean of the char_vect is", mean_char_vec)
cat("The mean of the factor_vec is", mean_factor_vec)
```

The reason for this may be that I used numbers 1, 2, and 3 to create the char_vec, so after conversion, it can be calculated. Additionally, the factor vector can be transformed into numeric values using the as.numeric function.